Guided Proofreading of Automatic Segmentations for Connectomics\\~\\\textit{Supplemental Material}

### 2017-11-14 paper/conclusion.tex
Restructure rebuttals.
Several changes from the rebuttal.
James edits

%The task of automatic cell boundary segmentation is difficult, and trying to improve such segmentations automatically as a post-process through merge and split error correction is, in principle, no different than trying to improve the underlying cell boundary segmentation. Due to the task difficulty, manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task. Humans are the bottleneck and minimizing the manual labor is the goal.
%We have trained classifiers to find merge and split errors in automatic segmentations of connectomics data. We then reduce the correction of these errors to simple yes/no decisions. This allows proofreading with better performance than existing systems.
%Our experiments also show that automatic proofreading works. This has the potential to further reduce the manual labor and will be the target of future research. To encourage testing of our proposed architecture and replication of our experiments, we provide our framework and data as free and open research at (link omitted for review).
%Minimizing manual labor is the goal when proofreading large automatic segmentations. Our classifiers suggest potential errors and corrections better than existing systems. This is especially important for novice users. Novices report difficulties when using fully interactive software but are invaluable to proofread the shear amounts of connectomics data.
%Our experiments also show that automatic proofreading works. This has the potential to further reduce human involvement and will be the target of future research. We provide our framework and data as free and open research at (link omitted for review).
Humans are the bottleneck when proofreading segmentation data and minimizing the manual labor is the goal. Our classifiers suggest potential errors and corrections better than existing methods. This reduces the time spent finding and correcting errors.
Our experiments also show that automatic proofreading has potential to further reduce human involvement. This will be the target of future research. We provide our framework and data as free and open research at (link omitted for review).

>>>>

%The task of automatic cell boundary segmentation is difficult, and trying to improve such segmentations automatically as a post-process through merge and split error correction is, in principle, no different than trying to improve the underlying cell boundary segmentation. Due to the task difficulty, manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task. Humans are the bottleneck and minimizing the manual labor is the goal.
%We have trained classifiers to find merge and split errors in automatic segmentations of connectomics data. We then reduce the correction of these errors to simple yes/no decisions. This allows proofreading with better performance than existing systems.
%Our experiments also show that automatic proofreading works. This has the potential to further reduce the manual labor and will be the target of future research. To encourage testing of our proposed architecture and replication of our experiments, we provide our framework and data as free and open research at (link omitted for review).
%Minimizing manual labor is the goal when proofreading large automatic segmentations. Our classifiers suggest potential errors and corrections better than existing systems. This is especially important for novice users. Novices report difficulties when using fully interactive software but are invaluable to proofread the shear amounts of connectomics data.
%Our experiments also show that automatic proofreading works. This has the potential to further reduce human involvement and will be the target of future research. We provide our framework and data as free and open research at (link omitted for review).

Manual proofreading of connectomics segmentations is currently necessary, but it is a time consuming and error-prone task. We attempt to minimize manual labor and reduce the human bottleneck. Our classifiers can detect errors and suggest potential corrections to automatically improve segmentations, but performance can increase with guided human attention. Our approach makes it easier for both novices and experts to proofread successfully, and is significantly better than the existing baseline at this task. This helps reduces the human time spent finding and correcting errors, and so makes it faster to generate new ground truth label data. Ultimately, this moves us closer to automatic proofreading. (source/data URL omitted for review).%\url{http://rhoana.org/guidedproofreading/}.

%Our experiments also show that automatic proofreading has potential to further reduce human involvement. We provide our framework and data as free and open research at (link omitted for review).%\url{http://rhoana.org/guidedproofreading/}.

%\section*{Acknowledgements}
%We would like to thank Stephen Plaza for detailed explanations of focused proofreading and Toufiq Parag for the configuration of the NeuroProof classifier.

### 2017-11-14 paper/method.tex
James edits

\CHANGED{To find merge errors, we generate candidate splits within a label segment and use our split error classifier to rate them. 
%If the classifier yields a result close to 0, meaning the candidate split is actually likely to be a correct one, then we assume that the label has been merged in error and that this candidate split will fix the merge error.
If the classifier yields a result close to 0, the candidate split is likely to be correct. We then use it to fix the merge error.}

@@

%For each segmentation label, we dilate the label by 20 pixel and generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. We perform watershed on the inverted grayscale EM image. This yields 50 candidate splits.
To generate candidate splits for each segmentation label, we create 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary.
\CHANGED{%For each segmentation label, we generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. 
As preprocessing, we dilate the label by 20 pixel which is motivated by our observation that the generated splits tend to attach to real membrane boundaries. These boundaries are then individually rated using our split error classifier. Fig. \ref{fig:merge_error} illustrates this procedure. Pseudo code is available as supplemental material to promote understanding.}

>>>>

\CHANGED{To find merge errors, we generate candidate splits within a label segment and use our split error classifier to rate them. 
%If the classifier yields a result close to 0, meaning the candidate split is actually likely to be a correct one, then we assume that the label has been merged in error and that this candidate split will fix the merge error.
If the classifier yields a result close to 0, the candidate split is likely to be correct. Then, we use it to fix the merge error.}

@@

%For each segmentation label, we dilate the label by 20 pixel and generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. We perform watershed on the inverted grayscale EM image. This yields 50 candidate splits.
To generate candidate splits for each segmentation label, we create 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary.
\CHANGED{%For each segmentation label, we generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. 
As preprocessing, we dilate the label by 20 pixels. This is motivated by our observation that the generated splits tend to attach to real membrane boundaries. These boundaries are then individually rated using our split error classifier (Fig.~\ref{fig:merge_error}).  Pseudo code is available in supplemental material.}

### 2017-11-14 paper/results.tex
James edits

\CHANGED{We present the first proofreading benchmark for the field of connectomics as an open research platform. We include representative connectomics data with ground truth labels, all results and participant demographics from the interactive experiments by Haehn~\etal~\cite{haehn_dojo_2014}, our complete results from this paper, as well as standardized metrics for comparing different proofreading approaches at (link omitted for review). We hope that this framework facilitates future developments and allows comparisons for conquering the important proofreading problem in connectomics.}

>>>>

\CHANGED{Along with our classifier code, we also present this evaluation scenario to the community as the first benchmark for proofreading in connectomics. We include representative connectomics data with ground truth labels, all participant results and demographics from the interactive experiments, our complete results from this paper, and standardized metrics for comparing different proofreading approaches. This framework will facilitate further comparisons to help make progress in connectomics (link omitted for review).}

### 2017-11-14 paper/supplemental/cremi.tex
James edits

Figure~\ref{fig:cremiAtrails} and~\ref{fig:cremiAboxplot} compare Plaza's focused proofreading and guided proofreading on the 5 sections of the CREMI A dataset.

>>>>

Figure~\ref{fig:cremiAtrails} and~\ref{fig:cremiAboxplot} compare Plaza's focused proofreading and guided proofreading on the five sections of CREMI A.

### 2017-11-14 paper/supplemental/leftcylinder.tex
James edits

\CHANGED{We use a single factor between-subject design with the factor being the proofreading method (GP, FP, or Dojo). Our hypothesis is that VI reduction is significantly better with GP than with other tools. For this, we treat VI as a continuous variable and use analysis of variance (ANOVA~\cite{shaffer1995}) followed by parametric tests (Welch's t-test~\cite{welch}).}

\CHANGED{\paragraph{AC4 subvolume.} For novice performance, we observe a significant effect ($\alpha = 0.05$) of which proofreading tool is used for the three conditions GP, FP, and Dojo [$F(2,27) = 6.446, p = 0.005$] when comparing the mean VI outcome. Post hoc comparisons (after Bonferroni correction) indicate that the mean VI for GP is significantly lower than for FP [$t_{27} = -2.7696, p = 0.0168$], and that the mean VI for GP is significantly lower than for Dojo [$t_{27} = -4.407, p < 0.001$]. This means that novices using GP perform significantly better than using FP and Dojo.
A similar trend is visible when comparing the expert performance between GP and FP as the change in mean VI of GP is significantly better ([$F(1,18) = 7.054, p = 0.016$] and [$t_{18} = -2.6559, p = 0.0216$]). For automatic selection with threshold, the difference in mean VI is very large and GP also performs significantly better ([$F(1,18) = 89.902, p < 0.001$] and [$t_{18} = 9.482, p < 0.001$]). The final VI scores of the selection oracle with GP and FP are very similar and the difference between them is not significant [$F(1,18) = 0.795, p = 0.384$]. However, the VI reduction rate of GP is much higher as seen in Fig.~\ref{fig:ac4trails} (right).}

\CHANGED{\paragraph{L. Cylinder.} The automatic selection with threshold yields similar results as on the other dataset and we observe a significant improvement when using GP instead of FP ([$F(1,98) = 26.676, p < 0.001$], post hoc comparison [$t_{98} = 5.1648, p < 0.001$]). The selection oracles of GP and FP result in very similar final VI scores and the difference is not significant [$F(1,98) = 0.071, p = 0.790$], but GP reaches minimum VI faster in $10,000$ corrections versus FP in $26,170$ corrections.}

>>>>

We use a single factor between-subject design with the factor being the proofreading method (GP, FP, or Dojo). Our hypothesis is that VI reduction is significantly better with GP than with other tools. For this, we treat VI as a continuous variable and use analysis of variance (ANOVA~\cite{shaffer1995}) followed by parametric tests (Welch's t-test~\cite{welch}).

\paragraph{AC4 subvolume.} For novice performance, we observe a significant effect ($\alpha=0.05$) of which proofreading tool is used for the three conditions GP, FP, and Dojo [$F(2,27) = 6.446, p = 0.005$] when comparing the mean VI outcome. Post hoc comparisons (after Bonferroni correction) indicate that the mean VI for GP is significantly lower than for FP [$t_{27} = -2.7696, p = 0.0168$], and that the mean VI for GP is significantly lower than for Dojo [$t_{27} = -4.407, p < 0.001$]. This means that novices using GP perform significantly better than using FP and Dojo.
A similar trend is visible when comparing the expert performance between GP and FP as the change in mean VI of GP is significantly better ([$F(1,18) = 7.054, p = 0.016$] and [$t_{18} = -2.6559, p = 0.0216$]). For automatic selection with threshold, the difference in mean VI is very large and GP also performs significantly better ([$F(1,18) = 89.902, p < 0.001$] and [$t_{18} = 9.482, p < 0.001$]). The final VI scores of the selection oracle with GP and FP are very similar and the difference between them is not significant [$F(1,18) = 0.795, p = 0.384$]. However, the VI reduction rate of GP is much higher (Fig.~6, main paper, right).

\paragraph{L. Cylinder.} The automatic selection with threshold yields similar results as on the AC4 dataset, and we observe a significant improvement when using GP instead of FP ([$F(1,98) = 26.676, p < 0.001$], post hoc comparison [$t_{98} = 5.1648, p < 0.001$]). The selection oracles of GP and FP result in very similar final VI scores and the difference is not significant [$F(1,98) = 0.071, p = 0.790$], but GP reaches minimum VI faster in $10,000$ corrections versus FP in $26,170$ corrections.

### 2017-11-14 paper/supplemental/userstudy.tex
James edits

\CHANGED{We integrate guided proofreading into an existing large data connectomics workflow. The web-based system is designed with a novice-friendly user interface (Fig. 5 in the paper, and the supplemental video). We show the current labeling of a cell boundary outline and its proposed correction overlayed on EM image data. The user cannot distinguish the current labeling from the proposed correction to avoid selection bias. We also show a solid overlay of the current and the proposed labeling. In addition, we show the image without overlays to provide an unoccluded view. User interaction is simple and involves one mouse click on either the current labeling or the correction. After interaction, the next potential error is shown.}

@@

After the experiment, we acquired subjective responses using the NASA-TLX task load index (Figure~\ref{fig:nasatxl}). We performed ANOVA to test for statistical significance~\cite{shaffer1995}. Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading but the analysis did not yield any significance. \CHANGED{This is unsurprising as the user interface was the same for both groups.}

>>>>

We integrate guided proofreading into an existing large data connectomics workflow. The web-based system is designed with a novice-friendly user interface (Fig. 5 in the paper, and the supplemental video). We show the current labeling of a cell boundary outline and its proposed correction overlayed on EM image data. The user cannot distinguish the current labeling from the proposed correction to avoid selection bias. We also show a solid overlay of the current and the proposed labeling. In addition, we show the image without overlays to provide an unoccluded view. User interaction is simple and involves one mouse click on either the current labeling or the correction. After interaction, the next potential error is shown.

@@

After the experiment, we acquired subjective responses using the NASA-TLX task load index (Figure~\ref{fig:nasatxl}). We performed ANOVA to test for statistical significance~\cite{shaffer1995}. Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading but the analysis did not yield any significance. This is unsurprising as the user interface was the same for both groups.
